\vspace{-3em} \includegraphics[width=.1\textwidth]{Figures/logo.png} \\ \includegraphics[width=4cm]{Figures/logotext.png} \\

### 2014-10-08 report/article_4.tex
report final for today
save report before latex env swap

@@

A full report with additional visualisations is online at {\bf
  \href{http://blm.io/datarea}{blm.io/datarea} }and scripts to
reproduce all analyses are available from {\bf
  \href{http://github.com/blmoore/summerdatachallenge}{github.com/blmoore/summerdatachallenge}}.

@@

@@

\setlength{\intextsep}{0em}
\begin{wrapfigure}{R}{.5\textwidth}
\vspace{1em}
\begin{center}
\includegraphics[width=.48\textwidth]{Figures/fractal.png}
\vspace{.5em}
\caption{ Fractal context of postcode SW18 4HU in Wandsworth, South London.}
\end{center}
\end{wrapfigure}

@@

\begin{wrapfigure}{l}{.2\textwidth}
\begin{center}
\includegraphics[width=.15\textwidth]{Figures/zoopla.png}
\includegraphics[width=.2\textwidth]{Figures/rightmove.jpg}
\caption*{ Example customer segments.}
\end{center}
\end{wrapfigure}

@@

\vspace{1em}
\begin{flushright}
{\small An enhanced overview of this entry is available online at: \href{http://blm.io/datarea}{blm.io/datarea}}
\end{flushright}

>>>>

\setlength{\intextsep}{0em}
\begin{wrapfigure}{R}{.3\textwidth}
%\vspace{-1em}
\centering
\includegraphics[width=.28\textwidth]{Figures/overview.png}
%\vspace{-1em}
\caption{ Mapped house sales, brightness is proportional to price.}
\end{wrapfigure}

@@

A full report with additional visualisations is online at {\bf
  \leavevmode\href{http://blm.io/datarea}{blm.io/datarea} }and scripts to
reproduce all analyses are available from {\bf
  \leavevmode\href{http://github.com/blmoore/summerdatachallenge}{github.com/blmoore/summerdatachallenge}}.

@@

%\setlength{\intextsep}{0em}
\begin{wrapfigure}[17]{L}{.45\textwidth}
%\vspace{-1em}
\centering
\includegraphics[width=.43\textwidth]{Figures/fractal.png}
\caption{ Fractal context of postcode SW18 4HU in Wandsworth, South London.}
%\vspace{35em}
\end{wrapfigure}

@@

@@

\begin{wrapfigure}{l}{.25\textwidth}
\begin{center}
\includegraphics[width=.18\textwidth]{Figures/zoopla.png}
\includegraphics[width=.23\textwidth]{Figures/rightmove.jpg}
\caption*{ Potential partners. }
\end{center}
\end{wrapfigure}

@@

\vspace{1em}
\begin{flushright}
{\small An enhanced overview of this entry is available online at: \leavevmode\href{http://blm.io/datarea}{blm.io/datarea}}
\end{flushright}
